Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-29 paper/main.tex
tweaks forgiveness paragraph based on marc's comments

Forgiveness in R. Axelrod's terms is a two round procedure. Though essentially
it is the strategy's ability to go from a \(DC\) to \(C\) aiming to achieve
mutual cooperation again, the only way TFT would end up in \(DC\), in
environments without noise, is if it had received a defection and it retaliated.
Following, an opponent's defection if the opponent were to ``apologise''
(resulting in a \(DC\) round), then TFT would forgive its opponent since mutual
cooperation is better than mutual defection.
As a result of the strategy's strong performance in both tournaments, and moreover in a
series of evolutionary experiments~\cite{Axelrod1981}, TFT was often
claimed to be a highly robust (and sometimes the most robust) strategy for the IPD.

>>>>

Forgiveness is a strategy's ability to go from a \(DC\) to \(C\) aiming to achieve
mutual cooperation again, the only way TFT would end up in \(DC\), in
environments without noise, is if it had received a defection and then retaliated.
Subsequently, TFT would forgive an opponent that apologises (in a \(DC\) round)
by returning to cooperation, since mutual cooperation is better than mutual defection.
As a result of the strategy's strong performance in both tournaments, and moreover in a
series of evolutionary experiments~\cite{Axelrod1981}, TFT was often
claimed to be a highly robust (and sometimes the most robust) strategy for the IPD.
